\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushright}
Ayush Shivhare \\
860-730-2832 \\
ayush.shivh@gmail.com \\
linkedin.com/in/ayushshiv \\
github.com/Shivhare-Ayush
\end{flushright}

\vspace{1em}

November 28, 2025

Hiring Team \\
Oracle Global Industry Unit \\
United States

\vspace{1em}

Dear Hiring Team,

I am writing to apply for the Undergraduate Software Engineer internship with Oracle’s Global Industry Unit for the Summer 2026 program (May–August 2026). I am currently pursuing a B.S. in Computer Science at the University of Texas at Dallas (expected December 2026), will be enrolled before and after the internship, reside in the United States, and do not require visa sponsorship.

GIU’s focus on building industry-specific cloud applications at scale strongly aligns with my interests and experience. I am proficient in Java and Python, and I have practical experience with SQL and JavaScript. In recent projects I implemented backend services and data pipelines, designed RESTful APIs, and containerized deployments to improve reliability and deployability. At Potion Cast I built ingestion and telemetry pipelines to support a live conversational AI installation, adding SQL-based reporting and production observability. At Nebula Labs I contributed to platform work serving 20,000+ users, implementing Docker-based deployments and CI/CD pipelines that improved release reliability.

My coursework and projects cover Algorithms, Data Structures, Databases, Machine Learning, Big Data concepts, and Object-Oriented Programming. I have hands-on exposure to microservices architecture and container platforms (Docker), and I’m familiar with cloud deployments and service orchestration patterns. I have completed practical internships and project work that required end-to-end engineering — design, implementation, testing, and debugging — and can complete programming assignments independently in Java and Python.

I am excited by the opportunity to join GIU, work on domain-specific cloud applications, and contribute to high-quality code and scalable systems. I bring strong collaboration skills, experience mentoring peers, and a willingness to learn new technologies quickly. I can provide a transcript, project samples, and references upon request.

Thank you for your consideration; I look forward to the opportunity to contribute to Oracle GIU this summer.

Sincerely, \\
Ayush Shivhare

\end{document}
