\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushright}
Ayush Shivhare \\
860-730-2832 \\
ayush.shivh@gmail.com \\
linkedin.com/in/ayushshiv \\
github.com/Shivhare-Ayush
\end{flushright}

\vspace{1em}

December 24, 2025

Hiring Team \\
Tesla \\
United States

\vspace{1em}

Dear Hiring Team,

I am applying for a Summer 2026 Software Engineering internship at Tesla. I am a B.S. Computer Science student at the University of Texas at Dallas (expected December 2026) and am eligible to work in the U.S. without sponsorship. I’m energized by Tesla’s pace of innovation and the opportunity to build production systems that directly impact safety, quality, and customer experience at scale.

My recent work focuses on reliable, real-time systems and production delivery. At Potion Cast I engineered a low-latency conversational AI backend in Python, integrating OpenAI/ElevenLabs with Google Cloud and Firebase, optimizing REST endpoints for responsiveness, and instrumenting logging/metrics for a live public deployment. At Nebula Labs I led engineering for a platform serving 40,000+ users, implementing CI/CD for repeatable releases, and collaborating across product/analytics to maintain reliability as usage grew. In projects, I’ve built AI/data pipelines (Python, pandas, SQL), designed API-first services (React/Node.js), and practiced agile delivery.

I bring strong fundamentals (data structures, algorithms, OOP) and a production-first mindset: I write tests, add observability, and design for reliability. I’m comfortable learning new stacks quickly whether deeper systems programming, mobile or embedded components, or scaling data pipelines. I thrive in fast-moving teams, enjoy collaborating with designers and backend/data engineers, and like to validate work with performance and quality metrics.

I am available for the full Summer 2026 period and flexible on location. I would welcome the chance to contribute to high-impact engineering at Tesla and can share code samples and a transcript upon request.

Sincerely, \\
Ayush Shivhare

\end{document}
