\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{flushright}
Ayush Shivhare \\
860-730-2832 \\
ayush.shivh@gmail.com \\
linkedin.com/in/ayushshiv \\
github.com/Shivhare-Ayush
\end{flushright}

\vspace{1em}

November 17, 2025

Hiring Team \\
GM Financial \\
Fort Worth, TX

\vspace{1em}

Dear Hiring Team,

I am writing to apply for the 11-week Summer Internship at GM Financial (May 27 -- August 7). I am a B.S. Computer Science candidate at the University of Texas at Dallas (graduating December 2026) with hands-on experience building production services, cloud integrations, and DevOps pipelines. I’m excited by GM Financial’s focus on innovation and production-first engineering, and I’d welcome the chance to contribute to your data, web, and API initiatives while learning your security and DevOps practices.

At Potion Cast I built the backend for the ``Magic Eye'' interactive \textbf{conversational AI} attraction used in a live event. I integrated \textbf{OpenAI} and \textbf{ElevenLabs} with \textbf{Firebase} and \textbf{Google Cloud}, and I tuned \textbf{REST API} endpoints and logging to meet strict latency and reliability needs — delivering a stable, low-latency production experience for event attendees. That work taught me how to prioritize uptime, observability, and fast triage under real traffic.

As Head of Engineering at Nebula Labs I led efforts to make releases repeatable and scalable: I implemented disciplined \textbf{CI/CD} pipelines, containerized services with \textbf{Docker}, and standardized cloud deployments to support a high-traffic user base. I regularly participate in Agile/Scrum ceremonies (stand-ups, sprint planning, retros) to coordinate cross-functional priorities, and I run workshops and mentoring sessions to lift team delivery practices. These experiences map directly to your needs for building DevOps tooling and improving time-to-market while keeping production stable.

I am eager to contribute to vulnerability remediation and static-scanning efforts in your pipelines and to help extend DevOps tooling (pipelines, scanning, and monitoring) across teams. I bring a production-first mindset, demonstrable experience with cloud services and APIs, and strong presentation skills for stakeholder-facing demos. I am available for the summer internship period and look forward to the opportunity to discuss how my background aligns with GM Financial’s goals.

Thank you for your consideration. I would welcome the opportunity to speak with you and can provide references or a short demo of recent projects on request.

Sincerely,

Ayush Shivhare

\end{document}