\resumeSubheading
{Potion Cast}{Sep. 2025 -- Oct. 2025}
{Back-End Architecture Intern}{Austin, TX}
\resumeItemListStart
    \resumeItem{Situation: deliver a production-ready interactive "Magic Eye" for a live event with strict latency requirements. \textbf{Action/Result:} Integrated \textbf{OpenAI} and \textbf{ElevenLabs} with \textbf{Firebase}/\textbf{Google Cloud} and tuned \textbf{REST API} endpoints, delivering a low-latency, reliable system for the live event.}
    \resumeItem{Situation: support high-traffic, production operation. \textbf{Action/Result:} Added production-focused logging and endpoint optimizations to improve throughput and simplify triage during the event.}
\resumeItemListEnd

\resumeSubheading
{Nebula Labs}{Aug. 2024 -- Present}
{Head of Engineering}{Richardson, TX}
\resumeItemListStart
    \resumeItem{Situation: rapid user growth demanded scalable and reliable releases. \textbf{Action/Result:} Implemented \textbf{CI/CD} pipelines, containerized services with \textbf{Docker}, and automated code reviews, enabling support for \textbf{20,000+} users and faster incident triage.}
    \resumeItem{Drove agile project cycles and validated releases via continuous integration and Git-based versioning}
    \resumeItem{Technologies: React, Vercel, Docker, Git, CI/CD}
\resumeItemListEnd

\resumeSubheading
{Association for Computing Machinery (ACM)}{Dec. 2024 -- Present}
{Mentor Program Officer}{Richardson, TX}
\resumeItemListStart
    \resumeItem{Situation: students building cloud projects needed guidance on production practices. \textbf{Action/Result:} Mentored teams on scalable backend design and \textbf{REST APIs}, and delivered workshops on \textbf{CI/CD}, increasing deployment success and project quality.}
    \resumeItem{Situation: students required better presentation skills for demos. \textbf{Action/Result:} Delivered targeted workshops and one-on-one coaching to improve technical communication for stakeholder-facing presentations.}
\resumeItemListEnd


