\resumeSubHeadingListStart
  \resumeSubheading{Potion Cast}{Jun 2024 -- Present}{Backend Engineer}{Remote}
  \resumeItemListStart
    \resumeItem{\textbf{Situation}: Creator platform needed reliable backend for real-time features; \textbf{Task}: build and deploy scalable services. \textbf{Action}: developed \textbf{Python}/\textbf{Node.js} microservices, containerized with \textbf{Docker}, set up \textbf{GitHub Actions} for automated testing and deployment, and wrote integration tests. \textbf{Result}: enabled daily deploys and cut response time by ~\textbf{40\%}.}
    \resumeItem{\textbf{Situation}: Need to catch bugs before production; \textbf{Task}: reliable release process. \textbf{Action}: automated tests and health checks in \textbf{GitHub Actions} workflows; added logging for debugging. \textbf{Result}: reduced production issues by \textbf{70\%} and faster rollout cycles.}
  \resumeItemListEnd

  \resumeSubheading{Nebula Labs}{Jan 2024 -- May 2024}{Software Engineer Intern}{Dallas, TX}
  \resumeItemListStart
    \resumeItem{\textbf{Situation}: Monolithic codebase slowed feature iteration; \textbf{Task}: modularize and automate testing. \textbf{Action}: split services into \textbf{microservices} using \textbf{Python} and \textbf{Node.js}, containerized with \textbf{Docker}, wrote unit and integration tests, and set up \textbf{GitHub Actions}. \textbf{Result}: cut deployment time by \textbf{40\%} and enabled faster releases.}
    \resumeItem{\textbf{Situation}: Data scattered across logs; \textbf{Task}: centralize insights. \textbf{Action}: built \textbf{ETL} pipeline in \textbf{Python} to aggregate logs and metrics; created dashboards. \textbf{Result}: faster debugging and reduced time-to-resolution by \textbf{50\%}.}
  \resumeItemListEnd

  \resumeSubheading{ACM UTD}{Aug 2023 -- Dec 2023}{Technical Lead, Workshops}{Richardson, TX}
  \resumeItemListStart
    \resumeItem{\textbf{Situation}: New student developers unfamiliar with teamwork and deployment; \textbf{Task}: hands-on mentorship. \textbf{Action}: led workshops on \textbf{Git}, \textbf{GitHub}, \textbf{Docker}, \textbf{testing}, and API design; code reviewed PRs for best practices. \textbf{Result}: guided 40+ students; 10 projects shipped and demonstrated successfully.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
